### 2017-11-15 Draft2/Appendix.tex
Duplicate note
Restate the theorems

@@

\begin{proof}[Proof (Theorem \ref{thm:EquivalenceRelation})]
	Clearly, $\ExprNToInfty \dfrac{f}{f} = 1$, so $f \sim f$. Thus, $\sim$ is reflexive.

@@

\begin{proof}[Proof (Theorem \ref{thm:RemovesLowerOrderTerms})]
	Let $g = o(f)$. By definition, $\ExprNToInfty \dfrac{g}{f} = 0$. Since $\ExprNToInfty \dfrac{f}{f}$ and $\ExprNToInfty \dfrac{g}{f}$ both exist,
	\begin{align*}
	\ExprNToInfty \dfrac{f + g}{f} = \ExprNToInfty \dfrac{f}{f} + \ExprNToInfty \dfrac{g}{f} = 1 + 0 = 1
	\end{align*}
	It follows that $f + g = f + o(f) \sim f$.
\end{proof}

@@

\begin{proof}[Proof (Corollary \ref{coro:PlusConstant})]
	If $f$ is unbounded, then $c = o(f)$. Applying Theorem \ref{thm:RemovesLowerOrderTerms}, $f + c \sim f$.
\end{proof}

@@

\begin{proof}[Proof (Theorem \ref{thm:MergesOverOps})]
	Let $\FuncQuotient = \dfrac{f + g}{\Tweak{f} + \Tweak{g}}$, and let $\FuncDenom = \Tweak{g} + \Tweak{g}^2 / \Tweak{f}$. $\FuncQuotient$ may be expressed as
	\begin{align*}
	\FuncQuotient &= \frac{(\Tweak{g} / \Tweak{f})(f + g)}{(\Tweak{g} / \Tweak{f})(\Tweak{f} + \Tweak{g})}\\
	&= \frac{\Tweak{g}(f / \Tweak{f}) + \Tweak{g}g / \Tweak{f}}{\FuncDenom}\\
	&= \frac{\Tweak{g}(f / \Tweak{f}) + (\Tweak{g}^2 / \Tweak{f})(g / \Tweak{g})}{\FuncDenom}\\
	&= \frac{\Tweak{g}}{d} \cdot \frac{f}{\Tweak{f}} + \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \frac{g}{\Tweak{g}}
	\end{align*}
	Now, consider that
	\begin{align*}
	\FuncQuotient - 1 &= \FuncQuotient - \frac{\FuncDenom}{\FuncDenom} = \FuncQuotient - \frac{\Tweak{g}}{\FuncDenom} - \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom}\\
	&= \frac{\Tweak{g}}{d} \cdot \frac{f}{\Tweak{f}} + \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \frac{g}{\Tweak{g}} - \frac{\Tweak{g}}{\FuncDenom} - \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom}\\
	&= \frac{\Tweak{g}}{d} \cdot \left( \frac{f}{\Tweak{f}} - 1 \right) + \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \left( \frac{g}{\Tweak{g}} - 1 \right)\\
	\ExprNToInfty \left( \FuncQuotient - 1 \right) &= \ExprNToInfty \left( \frac{\Tweak{g}}{d} \cdot \left( \frac{f}{\Tweak{f}} - 1 \right) + \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \left( \frac{g}{\Tweak{g}} - 1 \right) \right)\\
	&= \ExprNToInfty \left( \frac{\Tweak{g}}{d} \cdot \left( \frac{f}{\Tweak{f}} - 1 \right) \right) + \ExprNToInfty \left( \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \left( \frac{g}{\Tweak{g}} - 1 \right) \right)
	\end{align*}
	Since $\Tweak{g}$ and $\Tweak{g}^2 / \Tweak{f}$ sum to $\FuncDenom$ and all functions are positive, $\dfrac{\Tweak{g}}{\FuncDenom}$ and $\dfrac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom}$ are bounded between $0$ and $1$ as $n \to \infty$. From the given, $\ExprNToInfty \left( \dfrac{f}{\Tweak{f}} - 1 \right)$ and $\ExprNToInfty \left( \dfrac{g}{\Tweak{g}} - 1 \right)$ both exist and equal $0$. The limit of a bounded expression times one approaching $0$ is $0$; thus, both limits on the right-hand side are $0$.

@@

\begin{proof}[Proof (Corollary \ref{coro:BothSides})]
	This immediately follows from Theorem \ref{thm:MergesOverOps} by taking $\Tweak{g} = g$.
\end{proof}

@@

\begin{proof}[Proof (Theorem \ref{thm:SameBigOClass})]
	Let $r = \dfrac{f}{g}$. Since $\ExprNToInfty r = 1$, $r \leq 2$ for sufficiently large $n$. By definition, $\exists c : g \leq c h$ for sufficiently large $n$, where $c$ is a positive constant. Then, $f = rg \leq rc h \leq 2c h$ for sufficiently large $n$. Thus, $f = O(h)$.
\end{proof}

@@

\begin{proof}[Proof (Theorem \ref{thm:InterchangeableInInequality})]
	By definition, $\ExprNToInfty \dfrac{f}{\Tweak{f}} = 1$ and $\ExprNToInfty \dfrac{\Tweak{f}}{\TweakSecond{f}} < 1$. Since both limits exist,
	\begin{align*}
	\ExprNToInfty \frac{f}{\TweakSecond{f}} = \left( \ExprNToInfty \frac{f}{\Tweak{f}} \right) \left( \ExprNToInfty \frac{\Tweak{f}}{\TweakSecond{f}} \right) < 1 \cdot 1 = 1
	\end{align*}
	It follows that $f \FluteLess \TweakSecond{f}$.

@@

\begin{proof}[Proof (Theorem \ref{thm:BothSidesInequality})]
	Suppose that $f \FluteLess g$. By definition, $\ExprNToInfty \dfrac{f}{g} < 1$. For any positive function $h$, $\ExprNToInfty \dfrac{fh}{gh} < 1$ and $\ExprNToInfty \dfrac{f / h}{g / h} < 1$, so respectively $fh \FluteLess gh$ and $\dfrac{f}{h} \FluteLess \dfrac{g}{h}$.

@@

\begin{proof}[Proof (Theorem \ref{thm:BothSidesInequalityAdd})]
	Assume that $n$ is arbitrarily large. Since $\dfrac{f}{h}$ has a positive limit, it is bounded below by some positive constant $c_1$. Rearranging, $c_1 h \leq f$. From $f \FluteLess g$, it follows that $f < g$ for sufficiently large $n$. Since $g = O(h)$, $\exists c_2 : g \leq c_2 h$. Combining these inequalities, I receive $c_1 h \leq f < g \leq c_2 h$. From this, it is clear that $c_1 < c_2$.

>>>>

{\HdrNote} In the following theorems and their proofs, variables with the letters $f$, $g$, or $h$ denote functions that, for sufficiently large $n$, are positive and non-decreasing.

@@

\begin{reptheorem}{thm:EquivalenceRelation}
	$\sim$ is reflexive, transitive, and symmetric.
\end{reptheorem}

\begin{proof}
	Clearly, $\ExprNToInfty \dfrac{f}{f} = 1$, so $f \sim f$. Thus, $\sim$ is reflexive.

@@

\begin{reptheorem}{thm:RemovesLowerOrderTerms}
	$f + o(f) \sim f$.
\end{reptheorem}

\begin{proof}
	Let $g = o(f)$. By definition, $\ExprNToInfty \dfrac{g}{f} = 0$. Since $\ExprNToInfty \dfrac{f}{f}$ and $\ExprNToInfty \dfrac{g}{f}$ both exist,
	\begin{align*}
	\ExprNToInfty \dfrac{f + g}{f} = \ExprNToInfty \dfrac{f}{f} + \ExprNToInfty \dfrac{g}{f} = 1 + 0 = 1
	\end{align*}
	It follows that $f + g = f + o(f) \sim f$.
\end{proof}

@@

\begin{repcorollary}{coro:PlusConstant}
	If $f$ is unbounded, then $f + c \sim f$ for any constant $c$.
\end{repcorollary}

\begin{proof}
	If $f$ is unbounded, then $c = o(f)$. Applying Theorem \ref{thm:RemovesLowerOrderTerms}, $f + c \sim f$.
\end{proof}

@@

\begin{reptheorem}{thm:MergesOverOps}
	If $f \sim \Tweak{f}$ and $g \sim \Tweak{g}$, then
	\begin{align*}
	f + g &\sim \Tweak{f} + \Tweak{g}\\
	fg &\sim \Tweak{f}\Tweak{g}\\
	\frac{f}{g} &\sim \frac {\Tweak{f}} {\Tweak{g}}
	\end{align*}
\end{reptheorem}

\begin{proof}
	Let $\FuncQuotient = \dfrac{f + g}{\Tweak{f} + \Tweak{g}}$, and let $\FuncDenom = \Tweak{g} + \Tweak{g}^2 / \Tweak{f}$. $\FuncQuotient$ may be expressed as
	\begin{align*}
	\FuncQuotient &= \frac{(\Tweak{g} / \Tweak{f})(f + g)}{(\Tweak{g} / \Tweak{f})(\Tweak{f} + \Tweak{g})}\\
	&= \frac{\Tweak{g}(f / \Tweak{f}) + \Tweak{g}g / \Tweak{f}}{\FuncDenom}\\
	&= \frac{\Tweak{g}(f / \Tweak{f}) + (\Tweak{g}^2 / \Tweak{f})(g / \Tweak{g})}{\FuncDenom}\\
	&= \frac{\Tweak{g}}{d} \cdot \frac{f}{\Tweak{f}} + \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \frac{g}{\Tweak{g}}
	\end{align*}
	Now, consider that
	\begin{align*}
	\FuncQuotient - 1 &= \FuncQuotient - \frac{\FuncDenom}{\FuncDenom} = \FuncQuotient - \frac{\Tweak{g}}{\FuncDenom} - \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom}\\
	&= \frac{\Tweak{g}}{d} \cdot \frac{f}{\Tweak{f}} + \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \frac{g}{\Tweak{g}} - \frac{\Tweak{g}}{\FuncDenom} - \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom}\\
	&= \frac{\Tweak{g}}{d} \cdot \left( \frac{f}{\Tweak{f}} - 1 \right) + \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \left( \frac{g}{\Tweak{g}} - 1 \right)\\
	\ExprNToInfty \left( \FuncQuotient - 1 \right) &= \ExprNToInfty \left( \frac{\Tweak{g}}{d} \cdot \left( \frac{f}{\Tweak{f}} - 1 \right) + \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \left( \frac{g}{\Tweak{g}} - 1 \right) \right)\\
	&= \ExprNToInfty \left( \frac{\Tweak{g}}{d} \cdot \left( \frac{f}{\Tweak{f}} - 1 \right) \right) + \ExprNToInfty \left( \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \left( \frac{g}{\Tweak{g}} - 1 \right) \right)
	\end{align*}
	Since $\Tweak{g}$ and $\Tweak{g}^2 / \Tweak{f}$ sum to $\FuncDenom$ and all functions are positive, $\dfrac{\Tweak{g}}{\FuncDenom}$ and $\dfrac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom}$ are bounded between $0$ and $1$ as $n \to \infty$. From the given, $\ExprNToInfty \left( \dfrac{f}{\Tweak{f}} - 1 \right)$ and $\ExprNToInfty \left( \dfrac{g}{\Tweak{g}} - 1 \right)$ both exist and equal $0$. The limit of a bounded expression times one approaching $0$ is $0$; thus, both limits on the right-hand side are $0$.

@@

\begin{repcorollary}{coro:BothSides}
	A $\sim$ relation is preserved when both sides are added, multiplied, or divided by the same positive quantity.
\end{repcorollary}

\begin{proof}
	This immediately follows from Theorem \ref{thm:MergesOverOps} by taking $\Tweak{g} = g$.
\end{proof}

@@

\begin{reptheorem}{thm:SameBigOClass}
	If $f \sim g$ and $g = O(h)$, then $f = O(h)$.
\end{reptheorem}

\begin{proof}
	Let $r = \dfrac{f}{g}$. Since $\ExprNToInfty r = 1$, $r \leq 2$ for sufficiently large $n$. By definition, $\exists c : g \leq c h$ for sufficiently large $n$, where $c$ is a positive constant. Then, $f = rg \leq rc h \leq 2c h$ for sufficiently large $n$. Thus, $f = O(h)$.
\end{proof}

@@

\begin{reptheorem}{thm:InterchangeableInInequality}
	If $f \sim \Tweak{f}$ and $\Tweak{f} \FluteLess \TweakSecond{f}$, then $f \FluteLess \TweakSecond{f}$. If $g \sim \TweakSecond{g}$ and $\Tweak{g} \FluteLess \TweakSecond{g}$, then $\Tweak{g} \FluteLess g$.\\
	These statements also hold for $\FluteLeq$.
\end{reptheorem}

\begin{proof}
	By definition, $\ExprNToInfty \dfrac{f}{\Tweak{f}} = 1$ and $\ExprNToInfty \dfrac{\Tweak{f}}{\TweakSecond{f}} < 1$. Since both limits exist,
	\begin{align*}
	\ExprNToInfty \frac{f}{\TweakSecond{f}} = \left( \ExprNToInfty \frac{f}{\Tweak{f}} \right) \left( \ExprNToInfty \frac{\Tweak{f}}{\TweakSecond{f}} \right) < 1 \cdot 1 = 1
	\end{align*}
	It follows that $f \FluteLess \TweakSecond{f}$.

@@

\begin{reptheorem}{thm:BothSidesInequality}
	A $\FluteLess$ inequality is preserved when both sides are multiplied or divided by the same positive quantity.\\
	This statement also holds for $\FluteLeq$.
\end{reptheorem}

\begin{proof}
	Suppose that $f \FluteLess g$. By definition, $\ExprNToInfty \dfrac{f}{g} < 1$. For any positive function $h$, $\ExprNToInfty \dfrac{fh}{gh} < 1$ and $\ExprNToInfty \dfrac{f / h}{g / h} < 1$, so respectively $fh \FluteLess gh$ and $\dfrac{f}{h} \FluteLess \dfrac{g}{h}$.

@@

\begin{reptheorem}{thm:BothSidesInequalityAdd}
	Suppose $f \FluteLess g$. If $\ExprNToInfty \dfrac{f}{h} > 0$ and $g = O(h)$, then $f + h \FluteLess g + h$.\\
	This statement also holds for $\FluteLeq$.
\end{reptheorem}

\begin{proof}
	Assume that $n$ is arbitrarily large. Since $\dfrac{f}{h}$ has a positive limit, it is bounded below by some positive constant $c_1$. Rearranging, $c_1 h \leq f$. From $f \FluteLess g$, it follows that $f < g$ for sufficiently large $n$. Since $g = O(h)$, $\exists c_2 : g \leq c_2 h$. Combining these inequalities, I receive $c_1 h \leq f < g \leq c_2 h$. From this, it is clear that $c_1 < c_2$.
